---
output:
  html_fragment: default
  html_document: default
---
## Tracking various advertisements across Social Media Platforms. 

This report produces a dynamic analysis of the advertisements observed across various social media platforms with data being collected through a google form and stored in a google sheet which is linked in this report using a CSV link.

---
title: My dynamic report
output: html_fragment
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=FALSE, message=FALSE, warning=FALSE, error=FALSE)
```

```{r load_packages}
library(tidyverse)
```

```{r import_data}
logged_data <- read_csv("https://docs.google.com/spreadsheets/d/e/2PACX-1vTw1jgd6Ddopt68SabX1ZwHXxscmkMmSllT-yX-tFOPew-SM81sYUXtu3N_pI9nYWTdPccM9zgipXLU/pub?output=csv")
```

```{r rename_columns}
latest_data <- logged_data %>%
  rename(
    Advertisement_duration = `How long was the advertisement (seconds)? Between 1 - 300 (seconds) only`,
    Advertisement_Social_Media = `Where did you see the advertisement?`,
    Advertisement_Topic = `What was the advertisement about?`
  )
```

```{r summary_values}
mean_duration <- mean(latest_data$Advertisement_duration, na.rm = TRUE)
maximum_duration <- max(latest_data$Advertisement_duration, na.rm = TRUE)
amount_of_advertisements <- length(latest_data$Advertisement_duration)
```

The average duration of advertisements was `r round(mean_duration)` seconds.  
The longest advertisement was `r maximum_duration` seconds long.  
A total of `r amount_of_advertisements` ads were observed.

```{r plot_platforms}
ggplot(latest_data, aes(x = Advertisement_Social_Media)) +
  geom_bar() +
  labs(title = "Number of advertisements per platform",
       x = "Social Media Platform",
       y = "Count") +
  theme_minimal()
```

```{r plot_topics}
ggplot(latest_data, aes(x = Advertisement_Topic)) +
  geom_bar() +
  labs(title = "Number of advertisements by topic",
       x = "Topic",
       y = "Count") +
  theme_minimal()
```







       



       












